---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ConfigINI

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/ConfigINI)](https://CRAN.R-project.org/package=ConfigINI)
[![Codecov test coverage](https://codecov.io/gh/DyfanJones/ConfigINI/graph/badge.svg)](https://app.codecov.io/gh/DyfanJones/ConfigINI)
[![ConfigINI status badge](https://dyfanjones.r-universe.dev/ConfigINI/badges/version)](https://dyfanjones.r-universe.dev/ConfigINI)
<!-- badges: end -->

Oringially developed with the paws.common package. A Fast INI Parser for R using Rcpp.

## Installation

You can install the development version of ConfigINI like so:

Github:
``` r
remotes::install_github("dyfanjones/ConfigINI")
```

r-universe:
```r
install.packages("ConfigINI", repos = c("https://dyfanjones.r-universe.dev", "https://cloud.r-project.org"))
```

## Example

This is a basic example which shows you how to solve a common problem:

### Read:
``` {r, basic_read_ini}
library(ConfigINI)

demo_ini <- system.file("demo.ini", package = "ConfigINI")
read_ini(demo_ini)
```

ConfigINI is also capible of reading some nested key value pairs:

```{r, nested_ini}
nested_ini <- system.file("nested.ini", package = "ConfigINI")
cat(readLines(nested_ini), sep = "\n")
```

The current ini package doesn't support this feature and instead will flatten out the nested key value pairs:

```{r, nested_ini_read_ini}
ini::read.ini(nested_ini)
```

The ConfigINI package will keep the nested key value pairs:

```{r, nested_read_ini}
ConfigINI::read_ini(nested_ini)
```

### Write:

``` {r, write_ini}
library(ConfigINI)

temp_file <- tempfile(fileext = ".ini")
# Create an example configuration list
config <- list(
  person = list(name = "John Doe", age = "30", city = "New York"),
  job = list(title = "Engineer", company = "ExampleCorp")
)

# Write the configuration to an INI file
write_ini(config, temp_file)

# Check the content of the created INI file
cat(readLines(temp_file), sep = "\n")

# clean up
unlink(temp_file)
```

## Benchmark:

Finally ConfigINI is pretty fast. Here is a quick comparison

```r
# get inih from r-universe for benchmark
install.packages("inih", repos = c("https://dyfanjones.r-universe.dev", "https://cloud.r-project.org"))
```

```{r, benchmark} 
demo_ini <- system.file("demo.ini", package = "ConfigINI")
(bm <- bench::mark(
  ConfigINI::read_ini(demo_ini),
  inih::read_ini(demo_ini),
  ini::read.ini(demo_ini),
  relative = TRUE
))

ggplot2::autoplot(bm)
```
